Notes on 10d Super Yang-Mills

### 2019-03-05 10d_SYM_Notes.tex
b edits

\title{Notes on 10d Super Yang-Mills}
\author{Chris Elliott, Pavel Safronov and Brian Williams}
\date{\today}

@@

>>>>

\title{Notes on 10d Super Yang-Mills}
\author{Chris Elliott, Pavel Safronov and Brian Williams}

\date{\today}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}

@@

\brian{I realized I'm still confused with the role of Baulieu's $h$-field. 
I really suspect it's different than the usual auxiliary field story. 
It seems like Baulieu doesn't even write down the apparent off-shell SUSY module structure. 
}
\brian{I think without ever introducing an auxiliary field we can obtain the following module structure.}

\def\oloc{\mathcal{O}_{loc}}

Let $\oloc^{BRST}$ and $\oloc^{BV}$ be the local functionals for the BRST and BV fields, respectively. 
The BRST operator endows $\oloc^{BRST}$ with the structure of a cochain complex, and the BV operator together with the BV bracket endow $\oloc^{BV}[-1]$ with the structure of a dg Lie algebra. 
Note that there is a map of dg Lie algebras
\[
\oloc^{BV}[-1] \to {\rm End}(\oloc^{BRST})
\]
sending a functional $I$ to the endomorphism $\{I,-\}$.

\def\cN{\mathcal{N}}

The cursory definition of the linear map
\[
\mf g_{\cN=1} \to {\rm End}(\oloc^{BRST})
\]
is not a map of Lie algebras. 
It fails to preserve the Lie bracket by a term proportional to the equations of motion in the field $\lambda$. 
I claim that Baulieu's introduction of the $h$-field does not resolve this issue. (We can see this by counting fermion number. 
The space where the failure for this to be a Lie map is $S_+$, yet we are only adding a scalar $h$ in the auxiliary, so there's no way.

Instead, what one should try is the following. 
(This doesn't ever use a holomorphic language, so maybe I'm making a silly mistake.)
There is an obvious lift of the linear map $\mf g_{\cN=1} \to {\rm End}(\oloc^{BRST})$ to the BV complex
\[
\mf g_{\cN=1} \to \oloc^{BV} [-1] .
\]
%The prescription for defining this map is simple. 
This is still, of course, not a map of dg Lie algebras.
However, I claim that there is an $L_\infty$ correction to this map.

Fix a basis $\{Q_\alpha\}$ of $S_+$ and write a general element of the form $Q_{\alpha} = \epsilon^\alpha Q_\alpha$.
The putative, linear action, of the element $Q$ on the BV complex is through functionals of the form
\[
\int \epsilon \lambda^* \sd F_A 
\]
where $\lambda^*$ denotes the anti-field to $\lambda$. 
I claim that we can correct the action by adding a quadratic term to the action that sends a pair $Q_1 \otimes Q_2$ to the functional
\[
\int \epsilon_1 \lambda^* \epsilon_2 \lambda^*  .
\]

In terms of an $L_\infty$ action, I'm saying that there is the usual linear map
\[
I^{(1)} : \mf g_{\cN=1} \to \oloc^{BV} 
\]
plus an $L_\infty$ correction of the form:
\[
I^{(2)} : \mf g_{\cN=1}^{\otimes 2} \to \oloc^{BV} [-2]  .
\]
You may ask why we have to stop there, but I don't have a great conceptual answer besides the computational fact that it seems like it works out. 
I claim that $I^{(1)} + I^{(2)}$ determines an off-shell action of $\mf g_{\cN=1}$ on the BV complex.

At the level of generators, we are proposing a new transformation law of the form 
\begin{align*}
\delta A &= \d c + \Gamma(\epsilon,\lambda) \\
\delta \lambda &= [c,\lambda] + \epsilon \sd F_A  \pm \# \epsilon (\epsilon \lambda^*)  \\
\delta \lambda^* &= \sd \partial \lambda + [c, \lambda^*] + \epsilon \sd A^*  .
\end{align*}
I've included terms coming from the BV operator (which have no $\epsilon$ dependence). 
The only new term is the last one in the transformation law for $\lambda$, $\epsilon (\epsilon \lambda^*)$.
